Just Add IFC! A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-03-02 paper/retrofit.tex
notation in retrofit.

The particular choice of communication primitives has been motivated by
inter-worker communication in web browser APIs~\Red{cite}, but
other choices such as blocking communication or labeled channels
would also be possible.

@@

\Red{TODO[ds]:
  - move the async recv to text and out of the figure
  - clarify discussion on exceptions
  - fix the toLabled
}
Finally, in Figure~\ref{fig:embedding},
we provide all of the rules responsible for actually carrying out the embedding.
The most important feature of this embedding is that every task maintains its own
copy of the target language global state and evaluation context, thus
enforcing isolation between various tasks.  In more detail:

@@

\begin{code}
ix1, ix2 <= brecv . ie @=
tab tab tab (IT (let tx = TI (ix1, ix2 <= recv. ie  (IT tx)) in tx))
conf tS te @= iconf iS (fullconf id il tS (iniEt te), ldots)
niconf iS id il ie @= iconf iS (fullconf id il tS (iniEi ie), ldots)
CE[e] -> iconf iS (it, ldots) @= CE[e] .-> iconf iS (sched step (it, ldots))
\end{code}

@@

\begin{align*}
    & |let i = TI (sandbox (x, i' <= brecv . (IT (!(TI x)))))| \\
    & |in TI (send (IT (ref true)))|
\end{align*}

@@

\begin{align*}
    & |toLabeled l te @= | \\
    & |tab let pid = taskId; | \\
    & |tab let i = TI (sandbox (IT (TI (setLabel l); TI (send pid l (IT te)))))| \\
    & |tab in (\ _ . TI (setLabel l); TI ( x, _ <= recv . x ))| \\
\end{align*}

>>>>

The particular choice of communication primitives has been motivated by
inter-worker communication in web browser APIs~\Red{cite}, but
other choices such as blocking communication or labeled channels
would also be possible.
We note, however, that blocking receive can be implemented using
our asynchronous primitives as follows:
\begin{code}
  brecvf ix1 ix2 ie @=
  tab tab tab (IT (let tx = TI (recvf ix1 ix2 ie (IT tx)) in tx))
\end{code}

@@

\Red{TODO[ds]:
  - clarify discussion on exceptions
  - fix the toLabled
}
Finally, in Figure~\ref{fig:embedding},
we provide all of the rules responsible for actually carrying out the embedding.
The most important feature of this embedding is that every task maintains its own
copy of the target language global state and evaluation context, thus
enforcing isolation between various tasks.  In more detail:

@@

\begin{code}
conf tS te @= iconf iS (fullconf id il tS (iniEt te), ldots)
niconf iS id il ie @= iconf iS (fullconf id il tS (iniEi ie), ldots)
CE[e] -> iconf iS (it, ldots) @= CE[e] .-> iconf iS (sched step (it, ldots))
\end{code}

@@

\begin{align*}
    & |let i = TI (sandbox (brecvf x i' (IT (!(TI x)))))| \\
    & |in TI (send (IT (ref true)))|
\end{align*}

@@

\begin{align*}
    & |toLabeled l te @= | \\
    & |tab let i = taskId; | \\
    & |tab let j = TI (sandbox (IT (TI (setLabel l); TI (send i l (IT te)))))| \\
    & |tab in (\ _ . TI (setLabel l); TI (recvf x _ x unit))| \\
\end{align*}
